---
title: "Make final comments" 
author: "Kendra Wyant"
date: "`r lubridate::today()`"
format: 
  html: 
    embed-resources: true
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---   

## Notes

This script creates a dataframe for the second coder (KW). It is different than the initial file in three ways:

1. It removes video check in codes as these will not be included in the primary analyses due to a lower number of participants using this method.

2. It filters out comments that have less than 3 words. This decision was made based on numerous comments that offered no additional value from coding (e.g., "none", "na", "its fine").  

3. It cross checks Olivia's coding sheet for any additional excluded comments. 

4. It excludes comments from second burden survey (done in updated `mak_burden.qmd` script). See note below:

- Only 12 out of 245 participants completed a second burden survey. Only 2 people with a second survey completed the survey more than a month after their first survey and one of these people had NAs on comments for second survey. Decision to only keep first survey. 

**This file also serves as the final coded comments to be compared across coders 1 and 2 and to be used as inputs into all text analyses.**


## Set up
```{r}
#| include: false

options(conflicts.policy = "depends.ok")
library(tidyverse) 
library(janitor)

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")

theme_set(theme_classic())

path_prep <- format_path("studydata/risk2/data_processed/prep")
```

## Read in data

```{r}
qual_data <- read_csv(here::here(path_prep, "burden_qual.csv"),
                         show_col_types = FALSE) |> 
  glimpse()

codes_oc <- read_csv(here::here(path_prep, "qual_data_codes_OC.csv"),
                     show_col_types = FALSE) |> 
  glimpse()
```


## Remove rows not to be coded

Remove video comments
```{r}
qual_data <- qual_data |> 
  filter(!data == "video")
```

Remove Olivia's uncoded comments
```{r}
codes_oc_uncoded <- codes_oc |> 
  filter(is.na(acceptability)) |> 
  select(subid, user_survey_guid, data) |> 
  mutate(code = FALSE)

qual_data <- qual_data |> 
  left_join(codes_oc_uncoded, by = c("subid", "user_survey_guid", "data")) |> 
  mutate(code = if_else(is.na(code), TRUE, FALSE))

qual_data <- qual_data |> 
  filter(code)
```

Apply 3 word requirement on remaining comments
```{r}
qual_data <- qual_data |> 
  mutate(word_count = str_count(answer, '\\w+'))

qual_data |> 
  summarize(mean(word_count))
```

```{r}
qual_data |> 
  filter(word_count < 3) |> 
  pull(answer)

qual_data <- qual_data |> 
  filter(word_count >= 3) |> 
  select(-c(code, word_count)) |> 
  glimpse()
```


```{r}
qual_data |> 
  write_csv(here::here(path_prep, "final_comments.csv"))
```

