---
title: "Print all comments" 
author: "Kendra Wyant"
date: "`r lubridate::today()`"
format: 
  html: 
    embed-resources: true
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---   

## Notes

This file prints out the coded comments by theme and direction for final review by the 3 coders (KW, EL, CP).


```{r}
#| include: false


library(tidyverse) 
library(janitor)

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")

path_burden <- format_path("/risk2/data_processed/burden2")

codes <- read_csv(file.path(path_burden, "coded_comments.csv"),
                  show_col_types = FALSE)
```


### Benefits to self

```{r}
codes |> 
  filter(benefits_self != 0) |> 
  janitor::tabyl(benefits_self)
```

#### Positive
```{r}
codes |> 
  filter(benefits_self == "pos") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

#### Negative
```{r}
codes |> 
  filter(benefits_self == "neg") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

#### Neutral
```{r}
codes |> 
  filter(benefits_self == "neutral") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```



### Benefits to Others

```{r}
codes |> 
  filter(benefits_other != 0) |> 
  janitor::tabyl(benefits_other)
```

#### Positive
```{r}
codes |> 
  filter(benefits_other == "pos") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

#### Negative
```{r}
codes |> 
  filter(benefits_other == "neg") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

#### Neutral
```{r}
codes |> 
  filter(benefits_other == "neutral") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```


### Privacy

```{r}
codes |> 
  filter(privacy != 0) |> 
  janitor::tabyl(privacy)
```

#### Positive
```{r}
codes |> 
  filter(privacy == "pos") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

#### Negative
```{r}
codes |> 
  filter(privacy == "neg") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

#### Neutral
```{r}
codes |> 
  filter(privacy == "neutral") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```


### Feasibility

```{r}
codes |> 
  filter(feasibility != 0) |> 
  janitor::tabyl(feasibility)
```

#### Positive
```{r}
codes |> 
  filter(feasibility == "pos") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

#### Negative
```{r}
codes |> 
  filter(feasibility == "neg") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

#### Neutral
```{r}
codes |> 
  filter(feasibility == "neutral") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

#### Mixed
```{r}
codes |> 
  filter(feasibility == "mixed") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

### Research Context

```{r}
codes |> 
  filter(research_context != 0) |> 
  janitor::tabyl(research_context)
```

#### Positive
```{r}
codes |> 
  filter(research_context == "pos") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

#### Negative
```{r}
codes |> 
  filter(research_context == "neg") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

#### Neutral
```{r}
codes |> 
  filter(research_context == "neutral") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

### Technology

```{r}
codes |> 
  filter(technology != 0) |> 
  janitor::tabyl(technology)
```

#### Positive
```{r}
codes |> 
  filter(technology == "pos") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

#### Negative
```{r}
codes |> 
  filter(technology == "neg") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```

#### Neutral
```{r}
codes |> 
  filter(technology == "neutral") |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```


### Codes with no themes

395 comments with no themes endorsed

```{r}
codes |> 
  mutate(across(benefits_self:technology, ~ if_else(.x == 0, 0, 1)),
         sum = benefits_self + benefits_other + privacy + feasibility + research_context + technology) |> 
  filter(sum == 0) |> 
  select(comment_num, data, comment) |> 
  kableExtra::kable() |> 
   kableExtra::kable_classic()
```
