---
title: "Demographics" 
author: "Kendra Wyant"
date: "`r lubridate::today()`"
format: 
  html: 
    embed-resources: true
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---   

## Notes

This script calculates demographics for Burden2 study.

Outstanding issues:

- subid 1069 does not have intake survey - was able to impute race, age, and gender.   

From Madison: 1069 is the only person who didn't take intake because their phone was stolen right around 30 days on study.   

- Missing demographics for subid 1006 - was able to impute race, age, and gender 

From Susan: It was never determined why those questions didn't resolve for them. They had a lot of trouble with the app and surveys in general at the start. We do have some demographic data from them in their consent form, which you can grab via `enroll <- tidy_qualtrics("dem", token_qualtrics)`. We also know that gender = Man.

Primary variables for analyses:    

- race (Non-Hispanic White, Black, Hispanic, Other/Multiracial)
- gender (male, female)
- income (less than \$25000, more than \$25000)
- location (will be calculated in separate script)
- number of lapses on study up until the start time of the burden survey (separate script)

## Set up
```{r}
#| message: false

source(here::here("../analysis_risk2/functions/fun_star.R"))
library(tidyverse) 
library(janitor)

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/print_kbl.R?raw=true")

theme_set(theme_classic())

path_processed <- format_path("studydata/risk2/data_processed/shared")
path_burden <- format_path("studydata/risk2/data_processed/burden2")
path_admin <- "P:/administration"
```

## Read in data

Burden data
```{r}
burden <- read_csv(file.path(path_burden, "burden_quant.csv"),
                   show_col_types = FALSE)
```

Intake survey (with demographics)
```{r}
intake_survey <- read_csv(here::here(path_processed, "survey_intake_wide.csv"),
                         show_col_types = FALSE) 
```



## Num intake surveys per subid
```{r}
length(unique(intake_survey$subid)) # number of unique subids (246)
length(unique(burden$subid)) # number of unique subids (247)
```

Subid 1069 does not have intake
```{r}
burden |> 
  filter(!subid %in% intake_survey$subid)
```


## Missing data
```{r}
naniar::miss_var_summary(intake_survey) |> 
  print(n = 100)
```

Missing demographics for subid 1006 
```{r}
intake_survey |> 
  filter(subid == 1006) |> 
  glimpse()
```


## Create Demographics Tibble with variables of interest
```{r}
dem <- intake_survey |> 
  select(subid, starts_with("race"), -race_other_text_text, gender, orientation, income, 
         employment, education, age, romantic_status, med, whoassist_life_overdose)
```

Update race variables (temp remove 1006 since missing dem vars)   
```{r}
dem <- dem |> 
  filter(subid != 1006) |>
  rowwise() |> 
  mutate(race = case_when(sum(race_american_indian:race_pacific_islander, na.rm = TRUE) == 0 &
                            race_white == 1 ~ "Non-Hispanic White",
                          race_black == 1 & sum(race_american_indian:race_asian, na.rm = TRUE) == 0 &
                            sum(race_hispanic:race_white, na.rm = TRUE) == 0 ~ 
                            "Black/African American",
                          race_hispanic == 1 & sum(race_american_indian:race_black, na.rm = TRUE) == 0 &
                            sum(race_not_listed:race_white, na.rm = TRUE) == 0 ~ "Hispanic",
                          TRUE ~ "Other or Multiracial")) |> 
  ungroup()

table(dem$race)
```

Allow for people to be in more than one race category
```{r}
dem <- dem |> 
  rowwise() |> 
  mutate(race_multiple = case_when(sum(race_american_indian:race_pacific_islander, na.rm = TRUE) == 0 &
                            race_white == 1 ~ "Non-Hispanic White",
                          race_black == 1  ~ "Black/African American",
                          race_hispanic == 1 ~ "Hispanic",
                          TRUE ~ "Other")) |> 
  ungroup()

table(dem$race_multiple)
```



Add missing demographics for subid 1006 and 1069 

```{r}
dem <- dem |> 
  select(-c(race_american_indian:race_white)) |> 
  full_join(tibble(subid = c(1069, 1006),
                   gender = "Man", 
                   orientation = NA, 
                   income = NA, 
                   employment = NA,
                   education = NA, 
                   age = "36-45", 
                   romantic_status = NA, 
                   med = c(NA, "Medication taken daily (e.g., Suboxone, Methadone) and medication taken monthly (e.g., Vivitrol)"), 
                   whoassist_life_overdose = NA,
                   race = "Non-Hispanic White",
                   race_multiple = "Non-Hispanic White")) 
```

`r length(unique(dem$subid))` subids in final tibble.





## Check responses on other variables

### Gender

```{r}
tabyl(dem$gender) 
```

Make courser categories for gender

```{r}
dem <- dem |> 
  mutate(gender = if_else(gender == "Prefer not to say", NA, gender),
         gender = if_else(gender %in% c("Man", "Woman") | is.na(gender), 
                          gender, "other"))

tabyl(dem$gender)
```

### Orientation

```{r}
tabyl(dem$orientation) 
```

### Income

```{r}
tabyl(dem$income) 
```

### Employment

```{r}
tabyl(dem$employment) 
```

### Education

```{r}
tabyl(dem$education) 
```

### Age

```{r}
tabyl(dem$age) 
```

### Committed Relationship

```{r}
tabyl(dem$romantic_status) 
```


### Medication

```{r}
tabyl(dem$med) 
```

### Lifetime History of Overdose

```{r}
tabyl(dem$whoassist_life_overdose) 
```




## Save out tibble

```{r}
dem |> 
  write_csv(here::here(path_burden, "demographics.csv"))
```




