---
title: "Preregistration" 
author: "Kendra Wyant"
date: "`r June 12, 2026"
number-sections: false
format: 
 html: 
   toc: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(tidyposterior))
```

## Quantitative Analyses

### Interference

#### Between Subjects

2 linear models (daily updates and monthly updates)

interfere ~ 1 + gender_centered + race_centered + income_centered + geography_centered

Interpretation:

- Overall ratings of interference (are ratings, on average, different than neutral/0)
- Demographic effects (are ratings, on average, different across demographic groups)

#### Within Subjects
1 linear model (daily updates - monthly updates)

interfere_diff ~ 1 + gender_centered + race_centered + income_centered + geography_centered

Interpretation:

- Overall difference in ratings of interference by measure (are there relative differences in interference ratings by measure)
- Demographic effects (are differences in ratings of interference by measure, on average, different across demographic groups)


### Dislike

5 linear models (daily updates, monthly updates, gps, SMS/phone logs, SMS content)

dislike ~ 1 + gender_centered + race_centered + income_centered + geography_centered

Interpretation:

- Overall ratings of dislike (are ratings, on average, different than neutral/0)
- Demographic effects (are ratings, on average, different across demographic groups)


#### Within Subjects
10 linear models (daily updates - monthly updates; daily updates - gps; daily updates - sms/phone logs; daily updates - sms content; monthly updates - gps; monthly updates - sms/phone logs;    monthly updates - sms content; gps - sms/phone logs; gps - sms content; sms/phone logs - sms content)

dislike_diff ~ 1 + gender_centered + race_centered + income_centered + geography_centered

Interpretation:

- Overall difference in ratings of dislike by measure (are there relative differences in dislike ratings by measure)
- Demographic effects (are differences in ratings of dislike by measure, on average, different across demographic groups)


## Demo: Quantitative

Generate simulated data with the following variables: 

Integer values ranging from -2 to 2 skewed negatively

- daily_update_interfere 
- monthly_update_interfere
- daily_update_dislike
- monthly_update_dislike
- gps_dislike
- sms_phone_logs_dislike
- sms_content_dislike

Centered demographic variables (-.5, .5)

- gender 
- race
- income
- geography

```{r}
#| code-fold: TRUE

set.seed(102030)

n <- 100

data <- tibble(subid = seq(1, 100, 1),
               daily_update_interfere = sample(c(-2, -1, 0, 1, 2),
                                               n,
                                               replace = TRUE,
                                               prob = c(.40, .30, .15, .10, .05)),
               monthly_update_interfere = sample(c(-2, -1, 0, 1, 2),
                                                 n,
                                                 replace = TRUE,
                                                 prob = c(.40, .30, .15, .10, .05)),
               daily_update_dislike = sample(c(-2, -1, 0, 1, 2),
                                             n,
                                             replace = TRUE,
                                             prob = c(.45, .25, .15, .10, .05)),
               monthly_update_dislike = sample(c(-2, -1, 0, 1, 2),
                                               n,
                                               replace = TRUE,
                                               prob = c(.45, .25, .15, .10, .05)),
               gps_dislike = sample(c(-2, -1, 0, 1, 2),
                                    n,
                                    replace = TRUE,
                                    prob = c(.50, .25, .15, .07, .03)),
               sms_phone_logs_dislike = sample(c(-2, -1, 0, 1, 2),
                                               n,
                                               replace = TRUE,
                                               prob = c(.50, .25, .15, .07, .03)),
               sms_content_dislike = sample(c(-2, -1, 0, 1, 2),
                                            n,
                                            replace = TRUE,
                                            prob = c(.55, .20, .15, .07, .03)),
               gender = sample(c(-.5, .5),
                               n,
                               replace = TRUE,
                               prob = c(.50, .50)),
               race = sample(c(-.5, .5),
                               n,
                               replace = TRUE,
                               prob = c(.70, .30)),
               income = sample(c(-.5, .5),
                               n,
                               replace = TRUE,
                               prob = c(.50, .50)),
               geography = sample(c(-.5, .5),
                               n,
                               replace = TRUE,
                               prob = c(.60, .40))) |> 
  glimpse()
```


### Between Subjects: Daily Update Interference

- interpret overall effect (ratings different than neutral; intercept), gender effect, race effect, income effect, and  geography effect on interference rating.
```{r}
summary(lm(daily_update_interfere ~ 1 + gender + race + income + geography, 
           data = data))

data |> 
  ggplot(aes(x = daily_update_interfere)) +
  geom_histogram(bins = 5, color = "black", fill = "light blue") +
  scale_x_continuous(NULL,
                     breaks = c(-2, -1, 0, 1, 2), 
                     labels = c("Strongly disagree",
                                "Mildly disagree",
                                "Agree and disagree equally",
                                "Mildly agree",
                                "Strongly agree")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 1,
                                   vjust = 1))

```


### Within Subjects: Daily vs Monthly Update Interference

```{r}
data_within <- data |> 
  mutate(interfere_diff = daily_update_interfere - monthly_update_interfere)

summary(lm(interfere_diff ~ 1 + gender + race + income + geography, 
           data = data_within))
```



## Qualitative Analyses

### Overall Attitude
10 logistic regression models for each sensing method (daily update, monthly update,
gps, phone/sms logs, sms content) x valence (positive, negative) combination. 

*okay to count mixed in both positive and negative?*

attitude_positive ~ 1 + gender_centered + race_centered + income_centered + geography_centered

attitude_negative ~ 1 + gender_centered + race_centered + income_centered + geography_centered

Interpretation:

- Overall log-odds of positive/negative comment
- Demographic effects (are log-odds of positive/negative comments different by demographic group)

### Theme Analyses
50 logistic regression models for each theme (benefits to self, benefits to others, privacy, research context, and feasibility) x sensing method (daily update, monthly update,
gps, phone/sms logs, sms content) x valence (positive, negative) combination.

*Or 25 models only looking at presence of theme?*  

theme_positive ~ 1 + gender_centered + race_centered + income_centered + geography_centered

theme_negative ~ 1 + gender_centered + race_centered + income_centered + geography_centered

Interpretation:

- Overall log-odds of positive/negative comment for theme
- Demographic effects (are log-odds of positive/negative comments for theme different by demographic group)


## Demo: Qualitative

Generate simulated data with the following variables: 

Dichotomous (0/1) values for coded themes

- attitude_pos
- attitude_neg
- benefits_self_pos
- benefits_self_neg 

Centered demographic variables (-.5, .5)

- gender 
- race
- income
- geography

```{r}
#| code-fold: TRUE

set.seed(102030)

n <- 100

data <- tibble(subid = rep(1:n, 5),
               data = rep(c("daily_update",
                            "monthly_update",
                            "gps",
                            "sms_content",
                            "sms_phone_logs"), 
                          each = n),
               attitude_pos = sample(c(1, 0),
                                     n*5,
                                     replace = TRUE,
                                     prob = c(.60, .40)),
               attitude_neg = sample(c(1, 0),
                                     n*5,
                                     replace = TRUE,
                                     prob = c(.60, .40)), 
               benefits_self_pos = sample(c(1, 0),
                                          n*5,
                                          replace = TRUE,
                                          prob = c(.60, .40)),
               benefits_self_neg = sample(c(1, 0),
                                          n*5,
                                          replace = TRUE,
                                          prob = c(.20, .80)),
               gender = sample(c(-.5, .5),
                               n*5,
                               replace = TRUE,
                               prob = c(.50, .50)),
               race = sample(c(-.5, .5),
                               n*5,
                               replace = TRUE,
                               prob = c(.70, .30)),
               income = sample(c(-.5, .5),
                               n*5,
                               replace = TRUE,
                               prob = c(.50, .50)),
               geography = sample(c(-.5, .5),
                               n*5,
                               replace = TRUE,
                               prob = c(.60, .40))) |> 
  glimpse()
```




### Overall Attitude Analysis: Positive and Negative for Daily Update

```{r}
summary(lm(attitude_pos ~ 1 + gender + race + income + geography, 
           data = subset(data, data == "daily_update")))

summary(lm(attitude_neg ~ 1 + gender + race + income + geography, 
           data = subset(data, data == "daily_update")))
```

### Theme Analysis: Benfits to Self Positive and Negative for Daily Update

```{r}
summary(lm(benefits_self_pos ~ 1 + gender + race + income + geography, 
           data = subset(data, data == "daily_update")))

summary(lm(benefits_self_neg ~ 1 + gender + race + income + geography, 
           data = subset(data, data == "daily_update")))
```





